---
title: "Activity 0102 - RStudio and R Markdown"
author: "Nick Rozema"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 variables (columns). The variables are **dataset**, **x**, and **y**.

### Exercise 2


```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y is -0.0645.

### Exercise 3


```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y is -0.0630.

The correlation for the 'star' dataset is less negative (i.e. closer to 0) than that for the 'dino' dataset.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}

```

```{r}

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)