---
title: "Activity 0102 - RStudio and R Markdown"
author: "Nick Rozema"
date: "8/26/2019"
output: 
  html_document: 
    highlight: kate
    theme: cosmo
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 variables (columns). The variables are **dataset**, **x**, and **y**.

### Exercise 2


```{r plot-dino, fig.height=4, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y is -0.0645.

### Exercise 3


```{r plot-star, fig.height=4, fig.width=4}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y is -0.0630.

The correlation coefficient for the 'star' dataset is less negative (i.e. closer to 0) than that for the 'dino' dataset.

### Exercise 4


```{r plot-circle, fig.height=4, fig.width=4}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient between x and y is -0.0683.

The correlation coefficient for the 'circle' dataset is more negative (i.e. farther from 0) than that for the 'dino' dataset.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)

```{r plot-all, fig.height=6, fig.width=6}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
``` 

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
